---
title: "R Project 1 - Hello R"
author: "Matt Greene"
date: "Due Fed 3rd"
output: html_document
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

1846 rows and 3 columns. The variables are the dataset, the x-values, and the y-values.

### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Let's plot the data in the star dataset:


```{r plot-star, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

And next calculate the correlation between `x` and `y` in this dataset:
 
```{r cor-star}
dino_data %>%
  summarize(r = cor(x, y))
```

The correlation coefficient for this dataset is different from the dino dataset, but not by much. They are both weakly related.

### Exercise 4

Let's plot the data in the circle dataset:

```{r plot-circle, fig.height=3, fig.width=3}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

And next the correlation between 'x' and 'y' in this dataset:

```{r cor-circle}
dino_data %>%
  summarize(r = cor(x, y))

```

The correlation coefficient for this dataset is different from the dino dataset, but not by much. They are both weakly related.

### Exercise 5

Now we are going to plot all the datasets at once:

```{r}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
geom_point()+
facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
theme(legend.position = "none")
```

And now we can see the correlation coefficients:

```{r}
datasaurus_dozen %>%
group_by(dataset) %>%
summarize(r = cor(x, y)) %>%
print(13)
```

